Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Formatting tweaks

In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$. Variable $\state[{i}]$ gives the state of this skipper in flight $i$. The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{... actually, not first and not last.} (\ref{eq6}) or in the last time slot of the flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the skipper is in a bye (\ref{eq8}) and if all time slots in a flight are equal to -2 then the skipper has finished all his matches (\ref{eq9}).

>>>>

In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is
defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is
in a match with skipper $k$ at time $i$. Variable $\state[{i}]$ gives the state
of this skipper in flight $i$. The skipper can be in a match in the first time
slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{\ldots
actually, not first and not last.} (\ref{eq6}), or in the last time slot of the
flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the
skipper is in a bye (\ref{eq8}), and if all time slots in a flight are equal to
-2 then the skipper has finished all his matches (\ref{eq9}).
